---
title: "ITN Eval Metrics"
author: "Candace Savonen and Kate Isaac"
date: "2024-01-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
```

## Collaborations

### Load Collaborations Data

```{r}
collabs <- readr::read_tsv(file.path("data", "collabs.tsv"))
```

### All Collaborations

```{r}
nrow(collabs)

collabs %>% dplyr::count(ITN_ITCR_or_external) %>% 
  dplyr::mutate(perc = n/sum(n))
```

```{r}
collabs <- collabs %>% tidyr::separate_rows("Category", sep = ", ", ) %>% 
  dplyr::mutate(Category = trimws(Category)) %>% 
  dplyr::filter(Category != "?")

nrow(collabs)
```

```{r}
collabs %>% dplyr::count(Category) %>% 
  ggplot2::ggplot(ggplot2::aes(y = n, x = reorder(Category,-n), fill = Category)) +
  ggplot2::geom_bar(position = "dodge", stat = "identity") +
  ggplot2::theme_minimal() +
  ggplot2::theme(axis.text.x=ggplot2::element_text(angle=60, hjust=1), 
                 strip.text.x = ggplot2::element_text(size = 6),
                 legend.position="none", 
                 plot.margin = unit(c(.75,.5,.5,.5), "cm")) + 
  ggplot2::xlab("")

ggplot2::ggsave(file.path("plots", "itn_collaboration_types.png"), width = 7, height = 5)
```

### Only ITCR funded collaborations

```{r}

```

## Loqui

### Load Loqui Data

```{r}
loqui_usage <- readr::read_tsv(file.path("data", "loqui_usage.tsv"))
```

### Unique users of Loqui

```{r}
loqui_usage %>% count(email) %>% dplyr::pull(email) %>% length()
```

### Number of videos made with Loqui

```{r, message = FALSE}
loqui_usage %>% count(email) %>% dplyr::pull(n) %>% sum()
```

## Workshop Feedback Info & Data Visualizations

### Load Workshop data

```{r}
itcr_slido_data <- readRDS(file.path("data", "itcr_slido_data.RDS"))
```

```{r}
poll_data <- itcr_slido_data$`Polls-per-user` %>%
  janitor::clean_names()
```

### How likely would you be to recommend this workshop?

#### Percent of responses who responded with an 8 or higher when asked how likely they would be to recommend this workshop

```{r}
poll_data <- poll_data %>% 
     mutate(merged_likely_rec = if_else(is.na(how_likely_would_you_be_to_recommend_this_workshop), how_likely_would_you_be_to_recommend_this_workshop_2, how_likely_would_you_be_to_recommend_this_workshop))

scores_df <- table(as.numeric(poll_data$merged_likely_rec)) %>% 
  data.frame() %>%
  mutate(Var1 = as.numeric(as.character(Var1))) %>%
  group_by(Var1 >= 8) %>%
  summarize(n=sum(Freq)) %>% `colnames<-`(c("eightormore", "n"))

scores_df[which(scores_df$eightormore == TRUE),"n"]/sum(scores_df$n)
```

#### Net promoter score

```{r}

promoters_categories <- poll_data %>% 
  dplyr::mutate(merged_likely_rec = 
                  as.numeric(merged_likely_rec), 
                promoter = dplyr::case_when(
                  merged_likely_rec < 7 ~ "detractors", 
                  merged_likely_rec == 7 ~ "passives", 
                  merged_likely_rec == 8 ~ "passives", 
                  merged_likely_rec > 8 ~ "promoters", 
                  TRUE ~ NA)) %>% 
  dplyr::count(promoter)

promoter_sums <- promoters_categories$n
names(promoter_sums) <- promoters_categories$promoter
sum(promoter_sums, na.rm = TRUE)

# Net Promoter Score
promoter_sums["promoters"]/sum(promoter_sums, na.rm = TRUE)- promoter_sums["detractors"]/sum(promoter_sums, na.rm = TRUE)
```

#### Bar graph

```{r}
as.numeric(poll_data$merged_likely_rec) %>%
  ggplot2::qplot(geom = "bar") +
  ggplot2::geom_bar(fill = "#CBC3E3") +
  ggplot2::theme_classic() +
  ggplot2::labs(title = "How likely would you be to recommend this workshop?", y="count", x="rating")
  ggplot2::ggsave(file.path("plots", "itn_workshop_rec.png"), width = 5, height = 3)
```


### Workshop Relevance Feedback

```{r}
  poll_data_subset <- poll_data %>%
    dplyr::filter(how_likely_are_you_to_use_what_you_learned_in_your_daily_work %in% c("Extremely likely", "Likely", "Not very likely", "Somewhat likely", "Very likely")) #this subset to only 72 rows instead of 119

  poll_data_subset$how_likely_are_you_to_use_what_you_learned_in_your_daily_work <- factor(poll_data_subset$how_likely_are_you_to_use_what_you_learned_in_your_daily_work, levels = c("Not very likely",  "Somewhat likely", "Likely", "Very likely", "Extremely likely"))

   ggplot2::ggplot(poll_data_subset, ggplot2::aes(x = how_likely_are_you_to_use_what_you_learned_in_your_daily_work)) +
    ggplot2::geom_bar(stat = "count", fill = "#CBC3E3") +
    ggplot2::theme_classic() +
    ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
    ggplot2::labs(title = "How likely are you to use what you learned in your daily work?") +
    ggplot2::xlab("")
   ggplot2::ggsave(file.path("plots", "itn_relevance.png"), width = 6, height = 4)
```

### Wordclouds for Qualitative Workshop Feedback

```{r, results = 'hide'}
ud_model <- udpipe::udpipe_download_model(language = "english")
ud_model <- udpipe::udpipe_load_model(ud_model$file_model)
```

#### What did you like most about the workshop?

```{r}
results <- udpipe::udpipe_annotate(ud_model, x = poll_data$what_did_you_like_most_about_the_workshop) %>%
  as.data.frame() %>%
  dplyr::filter(upos %in% c("NOUN", "ADJ", "ADV")) %>%
  dplyr::mutate(lemma= tolower(lemma)) %>%
  dplyr::count(lemma)

wordcloud::wordcloud(words = results$lemma, freq=results$n,colors = c("#98fb98", "#83D475", "#355E3B"),
          min.freq = 3, scale = c(3, .4))
```

#### Please share any recommendations you have for improvements

```{r}
rec_results <- udpipe::udpipe_annotate(ud_model, x = poll_data$please_share_any_recommendations_you_have_for_improvements) %>%
  as.data.frame() %>%
  dplyr::filter(upos %in% c("NOUN", "ADJ", "ADV")) %>%
  dplyr::mutate(lemma= tolower(lemma)) %>%
  dplyr::count(lemma)

wordcloud::wordcloud(words = rec_results$lemma, freq=rec_results$n,colors = c("#98fb98", "#83D475", "#355E3B"),
          min.freq = 3, scale = c(4, .4))
```


### Estimate/tally number of workshop attendees per workshop
```{r}
#if user ID is NA, filter out
#if all values are NA, filter out (never answered a question)
# filter out Candace and Greg

filtered_poll_data <- poll_data %>%
  filter(!is.na(user_id)) %>% #header lines
  filter(!(user_name == "Greg C")) %>% #workshop leader
  filter(!(user_name == "Candace")) %>% #workshop leader
  select(!(starts_with("practice"))) #practice column, not actual feedback

filtered_poll_data <- filtered_poll_data[-1,] #remove first row cause that's still Greg according to `what_is_your_name_and_what_institution_are_you_from`
table(filtered_poll_data$event_name)

```

Note that the above tally is looking before I've filtered out rows where there are no responses.

### Get estimate of total number of workshop attendees, not unique
```{r}
filtered_poll_data <- filtered_poll_data[,which(colnames(filtered_poll_data) == "what_do_you_hope_to_learn_at_this_workshop"):ncol(filtered_poll_data)]  #look only at columns that are feedback
nrow(filtered_poll_data) - sum(rowSums(is.na(filtered_poll_data)) == ncol(filtered_poll_data)) #number responses total - number responses where there is no feedback

```

### Get number of unique workshop attendees
```{r}  
unique_emails <-
  unique(c(poll_data$please_submit_your_email_so_we_can_log_your_attendance,
           poll_data$whats_your_email,
           poll_data$what_is_your_email)
         ) %>% data.frame() %>% filter(grepl("@", .)) #filter out entries that aren't an email address

nrow(unique_emails)
```

### Get career stage of workshop registrants
```{r}
career_stage_counts <- readr::read_tsv(file.path("data", "career_stage_counts.tsv"))
career_stage_counts_subset <- career_stage_counts[c(1:5), c(1:11)]
df_to_plot <- data.frame(Stage = colnames(career_stage_counts_subset[2:10]), count = unlist(career_stage_counts_subset[5, c(2:10)]))
df_to_plot <- data.frame(Stage = colnames(career_stage_counts_subset[2:10]), count = unlist(career_stage_counts_subset[5, c(2:10)]), "Trainee" = c("yes","yes","no","no","no","yes","no","yes","yes"))
ggplot(df_to_plot, aes(x=reorder(Stage, -count), y=count, fill=Trainee)) +
  geom_bar(stat = "identity") +
  xlab("Career stage") +
  ylab("Number of registrees") +
  theme_bw() + 
  theme(panel.background = element_blank(), panel.grid = element_blank(), axis.text.x = element_text(angle = 45, hjust=1)) +
  scale_fill_manual(values = c("#440154", "#28ae80"))
ggsave(file.path("plots", "itn_workshop_registration_career_stage.png"), width = 5, height = 5)

```