---
title: "ITN Eval Metrics"
author: "Candace Savonen"
date: "2024-01-05"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float: true
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Set Up

```{r}
dir.create("data", showWarnings = FALSE)
dir.create("plots", showWarnings = FALSE)

set.seed(1234)

devtools::load_all("../metricminer/")
library("ggplot2")
library("dlstats")
library("magrittr")

source(file.path("local_auth_2.R"))
auth_from_secret("calendly", token = Sys.getenv("METRICMINER_CALENDLY"))

auth_from_secret("google",
                 refresh_token = Sys.getenv("METRICMINER_GOOGLE_REFRESH"),
                 access_token = Sys.getenv("METRICMINER_GOOGLE_ACCESS"),
                 cache = TRUE)

auth_from_secret("github", token = Sys.getenv("METRICMINER_GITHUB_PAT"))

ga_accounts <- get_ga_user()
calendly_account <- get_calendly_user()
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#CC79A7", "#F0E442")
```

## Collect online course data

```{r}
if (!file.exists(file.path("data", "itcr_ga_metric_data.RDS"))) {
  fhdsl_stats_list <- get_all_ga_metrics(account_id = ga_accounts$id[1])
  itcr_stats_list <- get_all_ga_metrics(account_id = ga_accounts$id[2])
  
  # There's some google analytics that aren't ITCR courses
  not_itcr <- c("hutchdatasci", "whoiswho", "MMDS", "FH Cluster 101", "AnVIL_Researcher_Journey")

  # Set up each data frame 
  ga_metrics <- dplyr::bind_rows(fhdsl_stats_list$metrics ,itcr_stats_list$metrics) %>%
  dplyr::filter(
    !(website %in%not_itcr)
    )
  saveRDS(ga_metrics, file.path("data","itcr_ga_metric_data.RDS"))
  
  ga_dims <- dplyr::bind_rows(fhdsl_stats_list$dimensions, itcr_stats_list$dimensions) %>%
  dplyr::filter(
    !(website %in% not_itcr)
    )
  saveRDS(ga_dims, file.path("data","itcr_ga_dims_data.RDS"))
  
  ga_link_clicks <- dplyr::bind_rows(fhdsl_stats_list$link_clicks,itcr_stats_list$link_clicks) %>%
  dplyr::filter(
    !(website %in% not_itcr)
    )
  saveRDS(ga_link_clicks, file.path("data","itcr_ga_link_click_data.RDS"))
  
} else {
  ga_metrics <- readRDS(file.path("data","itcr_ga_metric_data.RDS"))
  ga_dims <- readRDS(file.path("data","itcr_ga_dims_data.RDS"))
  ga_link_clicks <- readRDS(file.path("data","itcr_ga_link_click_data.RDS"))
}

# Collect Coursera numbers by hand -- there's no API
coursera_numbers <- c(
  "AI in Software" = 137,
  "Leadership Course" = 623,
  "Documentation and Usability Course" = 284,
  "Computing" = 931,
  "Reproducibility" = 359,
  "Advanced Reproducibility in Cancer Informatics" = 264, 
  "AI For Decision Makers" = sum(c(8, 27, 20, 39))
) %>%
  data.frame() %>%
  tibble::rownames_to_column("website") %>%
  dplyr::rename("total_coursera_enrollments"= ".")

# Collect Leanpub numbers by hand -- their API is limited
leanpub_numbers <- c(
  "AI in Software" = 7,
  "Leadership Course" = 32,
  "Documentation and Usability Course" = 26,
  "Computing" = 20,
  "Reproducibility" = 12,
  "Advanced Reproducibility in Cancer Informatics" = 15,
  "Choosing Genomic Tools" = 13, 
  "GitHub Automation for Scientists" = 2
) %>%
  data.frame() %>%
  tibble::rownames_to_column("website") %>%
  dplyr::rename("total_leanpub_enrollees"= ".")

audience_df <- c(
  "AI in Software" = "Software developers", 
  "NIH Data Sharing" = "Leadership",
  "AI For Decision Makers"= "Leadership",
  "ITN Website" = "Website",
  "Leadership Course" = "Leadership",
  "Documentation and Usability Course"= "Software developers", 
  "Computing" = "New to data",
  "Reproducibility" = "New to data",
  "Advanced Reproducibility in Cancer Informatics" = "Software developers", 
  "Ethical Data Handling" = "Leadership",
  "OTTR website"= "Website",
  "Choosing Genomic Tools" = "New to data", 
  "Overleaf Intro" = "Other", 
  "GitHub Automation for Scientists" = "Software developers") %>%
  data.frame() %>%
  tibble::rownames_to_column("website") %>%
  dplyr::rename("audience"= ".")

# Join this all together
itcr_course_data <- ga_metrics %>% 
  dplyr::left_join(coursera_numbers) %>%
  dplyr::left_join(leanpub_numbers) %>% 
  dplyr::left_join(audience_df)

readr::write_tsv(itcr_course_data, file.path("data", "itcr_course_metrics.tsv"))
```

## Get OTTR courses

```{r}

sync_yamls <- c(
  "https://raw.githubusercontent.com/jhudsl/OTTR_Template/main/.github/sync.yml", 
  "https://raw.githubusercontent.com/C-MOOR/C-MOOR_Template//main/.github/sync.yml", 
  "https://raw.githubusercontent.com/jhudsl/AnVIL_Template/main/.github/sync.yml",
  "https://raw.githubusercontent.com/datatrail-jhu/DataTrail_Template/main/.github/sync.yml"
)


extract_repos <- function(yaml) {
  content <- yaml::read_yaml(yaml) 
  repos <- unlist(purrr::map(content$group, "repos"))
  repos <- unlist(strsplit(repos, "\n"))
  return(repos)
}

all_ottr_repos <- unlist(lapply(sync_yamls, extract_repos))

ottr_df <- data.frame(repo_name = all_ottr_repos) %>%
  tidyr::separate(repo_name, into = c("organization", "repo"), sep = "\\/", remove = FALSE) %>% 
  dplyr::mutate(template = dplyr::case_when(
    stringr::str_detect(repo, "template|Template") ~ "template", 
    TRUE ~ "course"
  )) %>% 
  dplyr::distinct()

ottr_df %>% dplyr::count(organization)

ottr_df %>% 
  dplyr::filter(template == "course") %>% 
  dplyr::count()
```

## Collaboration Info

```{r}
collabs <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1-8vox2LzkVKzhmSFXCWjwt3jFtK-wHibRAq2fqbxEyo/edit#gid=0")

nrow(collabs)

collabs %>% dplyr::count(ITN_ITCR_or_external) %>% 
  dplyr::mutate(perc = n/sum(n))
```

```{r}
collabs <- collabs %>% tidyr::separate_rows("Category", sep = ", ", ) %>% 
  dplyr::mutate(Category = trimws(Category)) %>% 
  dplyr::filter(Category != "?")

collabs %>% dplyr::count(Category) %>% 
  ggplot2::ggplot(ggplot2::aes(y = n, x = reorder(Category,-n), fill = Category)) +
  ggplot2::geom_bar(position = "dodge", stat = "identity") +
  ggplot2::theme_minimal() +
  ggplot2::theme(axis.text.x=ggplot2::element_text(angle=60, hjust=1), 
                 legend.position="none") + 
  ggplot2::xlab("")

ggplot2::ggsave(file.path("plots", "itn_collaboration_types.png"), width = 4, height = 3)
```

```{r}
open_agenda <- readLines("ITCR OPEN Group Agenda.txt")

dates <- grep("20", open_agenda, value = TRUE)
dates <- gsub(" Meeting| meeting", "", dates)
month <- stringr::word(dates, sep = " ")
year <- stringr::word(dates, sep = " ", start = 2)

names <- grep("20", open_agenda)
attendance <- abs(names[1:length(names)] - c(names[2:length(names)], length(open_agenda)))


open_attendance <- data.frame(
  date = lubridate::ym(paste(year,"-", month)),
  attendance)

ggplot2::ggplot(open_attendance, ggplot2::aes(x = date, y = attendance)) + 
  ggplot2::geom_bar(stat = "identity", fill = "lightgreen") +
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
  ggplot2::xlab("") +
  ggplot2::geom_text(ggplot2::aes(label = attendance), size = 3, vjust = - 1) 
  ggplot2::ggsave(file.path("plots", "open_attendance.png"), width = 4, height = 3)
  
```


## Collect Loqui Video Creation User data

### Unique users of Loqui

```{r}
loqui_usage <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1G_HTU-bv2k5txExP8EH3ScUfGqtW1P3syThD84Z-g9k/edit#gid=0")
loqui_usage %>% count(email) %>% dplyr::pull(email) %>% length()
```

### Number of videos made with Loqui

```{r, message = FALSE}
loqui_usage %>% count(email) %>% dplyr::pull(n) %>% sum()
```

## Collect Calendly info 

```{r}
calendly_user <- get_calendly_user()
calendly_events <- list_calendly_events(user = calendly_user$resource$uri)

```

## Collect Workshop Feedback Info

```{r}
if (!file.exists(file.path("data", "itcr_slido_data.RDS"))) {
  itcr_drive_id <- "https://drive.google.com/drive/folders/0AJb5Zemj0AAkUk9PVA"
  itcr_slido_data <- get_slido_files(itcr_drive_id)

  saveRDS(itcr_slido_data, file.path("data", "itcr_slido_data.RDS"))
} else {
  itcr_slido_data <- readRDS(file.path("data", "itcr_slido_data.RDS"))
}
poll_data <- itcr_slido_data$`Polls-per-user` %>%
  janitor::clean_names()
```


```{r}
promoters_categories <- poll_data %>% 
  dplyr::mutate(how_likely_would_you_be_to_recommend_this_workshop = 
                  as.numeric(how_likely_would_you_be_to_recommend_this_workshop), 
                promoter = dplyr::case_when(
                  how_likely_would_you_be_to_recommend_this_workshop < 7 ~ "detractors", 
                  how_likely_would_you_be_to_recommend_this_workshop == 7 ~ "passives", 
                  how_likely_would_you_be_to_recommend_this_workshop == 8 ~ "passives", 
                  how_likely_would_you_be_to_recommend_this_workshop > 8 ~ "promoters")) %>% 
  dplyr::group_by(promoter) %>%
  dplyr::count(promoter)

promoter_sums <- promoters_categories$n
names(promoter_sums) <- promoters_categories$promoter
sum(promoter_sums)

# Net Promoter Score
promoter_sums["promoters"]/sum(promoter_sums)- promoter_sums["detractors"]/sum(promoter_sums)
```

## Data Visualizations

### How likely would you be to recommend this workshop?

```{r}
as.numeric(c(poll_data$how_likely_would_you_be_to_recommend_this_workshop, poll_data$how_likely_would_you_be_to_recommend_this_workshop_2)) %>%
  ggplot2::qplot(geom = "bar") +
  ggplot2::geom_bar(fill = "#CBC3E3") +
  ggplot2::theme_classic() +
  ggplot2::labs(title = "How likely would you be to recommend this workshop?")
  ggplot2::ggsave(file.path("plots", "itn_workshop_rec.png"), width = 4, height = 2)
```

### Workshop Relevance Feedback

```{r}
  poll_data <- poll_data %>%
    dplyr::filter(how_likely_are_you_to_use_what_you_learned_in_your_daily_work %in% c("Extremely likely", "Likely", "Not very likely", "Somewhat likely", "Very likely"))

  poll_data$how_likely_are_you_to_use_what_you_learned_in_your_daily_work <- factor(poll_data$how_likely_are_you_to_use_what_you_learned_in_your_daily_work, levels = c("Not very likely",  "Somewhat likely", "Likely", "Very likely", "Extremely likely"))

   ggplot2::ggplot(poll_data, ggplot2::aes(x = how_likely_are_you_to_use_what_you_learned_in_your_daily_work)) +
    ggplot2::geom_bar(stat = "count", fill = "#CBC3E3") +
    ggplot2::theme_classic() +
    ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
    ggplot2::labs(title = "How likely are you to use what you learned in your daily work?") +
    ggplot2::xlab("")
   ggplot2::ggsave(file.path("plots", "itn_relevance.png"), width = 4, height = 2)
```

### Wordclouds for Qualitative Workshop Feedback

```{r, results = 'hide'}
ud_model <- udpipe::udpipe_download_model(language = "english")
ud_model <- udpipe::udpipe_load_model(ud_model$file_model)
```

#### What did you like most about the workshop?

```{r}
results <- udpipe::udpipe_annotate(ud_model, x = poll_data$what_did_you_like_most_about_the_workshop) %>%
  as.data.frame() %>%
  dplyr::filter(upos %in% c("NOUN", "ADJ", "ADV")) %>%
  dplyr::mutate(lemma= tolower(lemma)) %>%
  dplyr::count(lemma)

wordcloud::wordcloud(words = results$lemma, freq=results$n,colors = c("#98fb98", "#83D475", "#355E3B"),
          min.freq = 3, scale = c(3, .4))
```

#### Please share any recommendations you have for improvements

```{r}
rec_results <- udpipe::udpipe_annotate(ud_model, x = poll_data$please_share_any_recommendations_you_have_for_improvements) %>%
  as.data.frame() %>%
  dplyr::filter(upos %in% c("NOUN", "ADJ", "ADV")) %>%
  dplyr::mutate(lemma= tolower(lemma)) %>%
  dplyr::count(lemma)

wordcloud::wordcloud(words = rec_results$lemma, freq=rec_results$n,colors = c("#98fb98", "#83D475", "#355E3B"),
          min.freq = 3, scale = c(4, .4))
```

## Get number of unique workshop attendees

```{r}
unique_emails <-
  unique(c(itcr_slido_data$`Polls-per-user`$`Please submit your email so we can log your attendance`,
           itcr_slido_data$`Polls-per-user`$`What's your email?`,
           itcr_slido_data$`Polls-per-user`$`What is your email?`))

length(unique_emails)
```

## Unique visitors to websites

```{r}
ggplot2::ggplot(itcr_course_data, ggplot2::aes(x = reorder(website, -activeUsers), y = activeUsers, fill = audience)) +
  ggplot2::geom_bar(stat = "identity") +
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
  ggplot2::xlab("") +
  ggplot2::geom_text(ggplot2::aes(label = activeUsers), size = 3, vjust = - 1) +
  ggplot2::ylim(c(0, 6000)) + 
  ggplot2::scale_fill_manual(values=cbPalette)
  ggplot2::ggsave(file.path("plots", "itn_website_visits.png"), width = 4, height = 3) 
```

## Table of user engagement

```{r}
user_totals <- ga_metrics %>% 
  janitor::clean_names() %>% 
  dplyr::select(website, active_users, average_session_duration) %>% 
  knitr::kable(digits=2, long_table = TRUE,padding = 2) # %>%
  #kable_styling(latex_options = c("striped", "scale_down"))

#user_totals %>%
  #kableExtra::save_kable(file.path("plots/course_user_table.pdf"))

user_totals
```

```{r}
user_engagement <- ga_metrics %>% 
  janitor::clean_names() %>% 
  dplyr::select(website, screen_page_views_per_user, sessions, screen_page_views, engagement_rate) %>% 
  knitr::kable(digits=2, long_table = TRUE, padding = 2) # %>%
  #kableExtra::kable_styling(latex_options = c("striped", "scale_down"))

#user_engagement %>%
#  kableExtra::save_kable("plots/course_engagement_table.pdf")

user_engagement
```


```{r}
itcr_course_data %>% janitor::clean_names() %>% 
  dplyr::select(website, screen_page_views_per_user, average_session_duration, event_count_per_user, engagement_rate, audience) %>% 
  tidyr::pivot_longer(!c(website, audience), 
                      names_to = "metric_name", 
                      values_to = "value") %>% 
  dplyr::filter(website != "OTTR website") %>% 
  dplyr::filter(website != "ITN Website") %>% 
  dplyr::mutate(website = dplyr::case_when(website == "Advanced Reproducibility in Cancer Informatics" ~ "Advanced Reproducibility", 
                                           TRUE ~ website)) %>% 
  ggplot2::ggplot(ggplot2::aes(y = value, x = website, fill = audience)) +
  ggplot2::geom_bar(position = "dodge", stat = "identity") +
  ggplot2::theme_minimal() +
  ggplot2::theme(axis.text.x=ggplot2::element_text(angle=60, hjust=1)) +
  ggplot2::facet_wrap(~metric_name, scales = "free_y") + 
  ggplot2::scale_fill_manual(values=cbPalette)

ggplot2::ggsave(file.path("plots", "itn_engagement_stats.png"), width = 6, height = 4)
```

## ITN Course and Website Traffic Overtime 

```{r}
web_traffic_overtime <- ga_dims %>% 
  dplyr::mutate(date = lubridate::ymd(paste0(year, "-", month, "-", day))) %>% 
  dplyr::mutate(month_year = lubridate::ym(paste0(year, "-", month))) %>% 
  dplyr::mutate(web_yn = dplyr::case_when(
    website == "ITN Website" ~ "ITN Website", 
    website != "ITN Website" ~ "ITN Online Course Website")) %>% 
  dplyr::left_join(audience_df)

traffic_plot <- web_traffic_overtime %>% 
  dplyr::filter(website != "ITN Website") %>%
  dplyr::filter(website != "OTTR website") %>% 
  dplyr::group_by(month_year) %>% 
  dplyr::count() %>% 
  ggplot2::ggplot(ggplot2::aes(y = n, x = month_year)) + 
  ggplot2::geom_bar(stat = "identity", fill = "pink") + 
  ggplot2::scale_x_date(date_labels = "%b %Y") + 
  ggplot2::ylab("Unique ITN Online Course Visitors") +
  ggplot2::xlab("") +
  ggplot2::theme_minimal() +
  ggplot2::theme(axis.text.x=ggplot2::element_text(angle=60, hjust=1))

ggplot2::ggsave(file.path("plots", "itn_course_traffic_plot.png"), width = 4, height = 3.5)
  
traffic_plot
```


```{r}
long_df <- itcr_course_data %>% dplyr::select(c("website", 
                                     "totalUsers",
                                     "total_coursera_enrollments", 
                                     "total_leanpub_enrollees", 
                                     "audience")) %>%
  tidyr::pivot_longer(!c(website, audience),
                                         names_to = "modality", 
                                         values_to = "learner_count") %>%
  dplyr::filter(website != "ITN Website") %>%
  dplyr::filter(website != "OTTR website") 
```


### Total learners from each modality

```{r}
long_df %>% 
  dplyr::group_by(modality, audience) %>% 
  dplyr::summarize(total_learners = sum(learner_count, na.rm = TRUE)) %>%
  dplyr::filter(audience != "Other") %>%
ggplot2::ggplot(ggplot2::aes(x = reorder(modality, -total_learners), y = total_learners, fill = audience)) +
  ggplot2::geom_bar(stat = "identity", na.rm = TRUE) +
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
  ggplot2::xlab("") +
  ggplot2::ylab("Visitors/Enrollees") +
  ggplot2::geom_text(ggplot2::aes(label = total_learners), size = 3, vjust = - 1, na.rm = TRUE) + 
  ggplot2::ylim(c(0, 4200)) + 
  ggplot2::facet_wrap(~audience) + 
  ggplot2::scale_fill_manual(values=cbPalette)

ggplot2::ggsave(file.path("plots", "itn_total_enrollments.png"), width = 4, height = 3)
```

### Total learners by course

```{r}  
long_df %>% 
  dplyr::group_by(website, audience) %>% 
  dplyr::summarize(total_learners = sum(learner_count, na.rm = TRUE)) %>%
  dplyr::filter(audience != "Other") %>%
ggplot2::ggplot(ggplot2::aes(y = total_learners, x = reorder(website, -total_learners), fill = audience)) + 
  ggplot2::geom_bar(stat = "identity") + 
  ggplot2::ylab("Total learners by course") +
  ggplot2::theme_minimal() +
  ggplot2::theme(axis.text.x=ggplot2::element_text(angle=60, hjust=1), 
                 strip.text.x = ggplot2::element_text(size = 8)) + 
  ggplot2::geom_text(ggplot2::aes(label = total_learners), size = 3, vjust = - 1, na.rm = TRUE) +
  ggplot2::ylim(c(0, 1800)) + 
  ggplot2::xlab("") + 
  ggplot2::scale_fill_manual(values=cbPalette)

ggplot2::ggsave(file.path("plots", "itn_total_learners_by_course.png"), width = 10, height = 5)
```

```{r}
learner_by_course %>% 
  dplyr::group_by(audience) %>%
  dplyr::summarize(total_learners = sum(total_learners, na.rm = TRUE))%>%
  dplyr::arrange(-total_learners) %>% 
  knitr::kable()
```

### Course traffic by course

```{r}
web_traffic_overtime %>% 
  dplyr::group_by(website, month_year, audience) %>% 
  dplyr::count() %>% 
  dplyr::filter(website != "ITN Website") %>% 
  dplyr::filter(website != "OTTR website") %>% 
  dplyr::left_join(audience_df) %>% 
ggplot2::ggplot(ggplot2::aes(y = n, x = month_year, fill = audience)) + 
  ggplot2::geom_bar(stat = "identity") + 
  ggplot2::scale_x_date(date_labels = "%b %Y") + 
  ggplot2::ylab("Unique ITN Website Learners Overtime") +
  ggplot2::theme_minimal() +
  ggplot2::theme(axis.text.x=ggplot2::element_text(angle=60, hjust=1), 
                 strip.text.x = ggplot2::element_text(size = 8)) + 
  ggplot2::facet_wrap(~website) + 
  ggplot2::scale_fill_manual(values=cbPalette)

ggplot2::ggsave(file.path("plots", "itn_course_traffic_plot_by_course.png"), width = 10, height = 5)
```

### Software engagement 

```{r}
web_traffic_overtime %>% 
  dplyr::group_by(website, month_year) %>% 
  dplyr::count() %>% 
  dplyr::filter(website %in% c("ITN Website", "OTTR website")) %>%
ggplot2::ggplot(ggplot2::aes(y = n, x = month_year)) + 
  ggplot2::geom_bar(stat = "identity", fill = "pink") + 
  ggplot2::scale_x_date(date_labels = "%b %Y") + 
  ggplot2::ylab("Unique ITN software website visitors") +
  ggplot2::theme_minimal() +
  ggplot2::theme(axis.text.x=ggplot2::element_text(angle=60, hjust=1), 
                 strip.text.x = ggplot2::element_text(size = 8)) + 
  ggplot2::facet_wrap(~website) 

ggplot2::ggsave(file.path("plots", "itn_software_website_traffic.png"), width = 10, height = 5)
```

### CRAN downloads

```{r}
 download_stats <- cran_stats(c("ottrpal", "conrad", "ari", "text2speech"))

 download_stats %>% dplyr::summarize(download_total = sum(downloads))

 download_stats %>% dplyr::group_by(package) %>%
   dplyr::summarize(download_total = sum(downloads))

sum(download_stats$downloads) + 426

if (!is.null(download_stats)) {
  print(head(download_stats))
  ggplot(download_stats, aes(end, downloads, group=package, color=package)) +
    geom_line() +
    geom_point() +
    scale_y_log10() + 
    theme_minimal()
  
  ggplot2::ggsave(file.path("plots", "itn_software_cran_downloads.png"), width = 10, height = 5)
 }


```

## Coursera

```{r}
ggplot2::ggplot(itcr_course_data %>% dplyr::filter(total_coursera_enrollments > 0), ggplot2::aes(x = reorder(website, -total_coursera_enrollments), y = total_coursera_enrollments, fill = audience)) +
  ggplot2::geom_bar(stat = "identity", na.rm = TRUE) +
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
  ggplot2::xlab("") +
  ggplot2::ylab("Coursera enrollments") +
  ggplot2::geom_text(ggplot2::aes(label = total_coursera_enrollments), size = 3, vjust = - 1, na.rm = TRUE) +
  ggplot2::ylim(c(0, 1200)) + 
  ggplot2::scale_fill_manual(values=cbPalette[-3])

  ggplot2::ggsave(file.path("plots", "itn_coursera_enrollments.png"), width = 4, height = 2)
```

## Leanpub

```{r}
ggplot2::ggplot(itcr_course_data %>% dplyr::filter(total_leanpub_enrollees > 0) , ggplot2::aes(x = reorder(website, -total_leanpub_enrollees), y = total_leanpub_enrollees, fill = audience)) +
  ggplot2::geom_bar(stat = "identity", na.rm = TRUE) +
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
  ggplot2::xlab("") +
  ggplot2::ylab("Leanpub enrollments") +
  ggplot2::geom_text(ggplot2::aes(label = total_leanpub_enrollees), size = 3, vjust = - 1, na.rm = TRUE) +
  ggplot2::ylim(c(0, 40)) + 
  ggplot2::scale_fill_manual(values=cbPalette)

ggplot2::ggsave(file.path("plots", "itn_leanpub_enrollments.png"), width = 4, height = 2)
```

### Session Info 

```{r}
sessionInfo()
```
