---
title: "ITN Eval Metrics"
author: "Candace Savonen"
date: "2024-01-05"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float: true
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Set Up

```{r}
dir.create("data", showWarnings = FALSE)
dir.create("plots", showWarnings = FALSE)
set.seed(1234)

devtools::load_all("../metricminer/")
# authorize("google")
# authorize("calendly")

ga_accounts <- get_ga_user()
calendly_account <- get_calendly_user()
```

## Collect online course data

```{r}
if (!file.exists(file.path("data", "itcr_ga_metric_data.RDS"))) {
  fhdsl_stats_list <- get_all_ga_metrics(account_id = ga_accounts$id[1])
  itcr_stats_list <- get_all_ga_metrics(account_id = ga_accounts$id[2])
  
  # There's some google analytics that aren't ITCR courses
  not_itcr <- c("hutchdatasci", "whoiswho", "MMDS", "FH Cluster 101", "AnVIL_Researcher_Journey")

  # Set up each data frame 
  ga_metrics <- dplyr::bind_rows(fhdsl_stats_list$metrics ,itcr_stats_list$metrics) %>%
  dplyr::filter(
    !(website %in%not_itcr)
    )
  saveRDS(ga_metrics, file.path("data","itcr_ga_metric_data.RDS"))
  
  ga_dims <- dplyr::bind_rows(fhdsl_stats_list$dimensions, itcr_stats_list$dimensions) %>%
  dplyr::filter(
    !(website %in% not_itcr)
    )
  saveRDS(ga_dims, file.path("data","itcr_ga_dims_data.RDS"))
  
  ga_link_clicks <- dplyr::bind_rows(fhdsl_stats_list$link_clicks,itcr_stats_list$link_clicks) %>%
  dplyr::filter(
    !(website %in% not_itcr)
    )
  saveRDS(ga_link_clicks, file.path("data","itcr_ga_link_click_data.RDS"))
  
} else {
  ga_metrics <- readRDS(file.path("data","itcr_ga_metric_data.RDS"))
  ga_dims <- readRDS(file.path("data","itcr_ga_dims_data.RDS"))
  ga_link_clicks <- readRDS(file.path("data","itcr_ga_link_click_data.RDS"))
}

# Collect Coursera numbers by hand -- there's no API
coursera_numbers <- c(
  "AI in Software" = 137,
  "Leadership Course" = 623,
  "Documentation and Usability Course" = 284,
  "Computing" = 931,
  "Reproducibility" = 359,
  "Advanced Reproducibility in Cancer Informatics" = 264
) %>%
  data.frame() %>%
  tibble::rownames_to_column("website") %>%
  dplyr::rename("total_coursera_enrollments"= ".")

# Collect Leanpub numbers by hand -- their API is limited
leanpub_numbers <- c(
  "AI in Software" = 7,
  "Leadership Course" = 32,
  "Documentation and Usability Course" = 26,
  "Computing" = 20,
  "Reproducibility" = 12,
  "Advanced Reproducibility in Cancer Informatics" = 15,
  "Choosing Genomic Tools" = 13
) %>%
  data.frame() %>%
  tibble::rownames_to_column("website") %>%
  dplyr::rename("total_leanpub_enrollees"= ".")

# Join this all together
itcr_course_data <- ga_metrics %>% 
  dplyr::left_join(coursera_numbers) %>%
  dplyr::left_join(leanpub_numbers)

readr::write_tsv(itcr_course_data, file.path("data", "itcr_course_metrics.tsv"))
```

## Collect Meeting Info from Calendly

```{r}
meetings <- list_calendly_events(user = calendly_account$resource$uri)
```

## Collect Loqui Video Creation User data

### Unique users of Loqui

```{r}
loqui_usage <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1G_HTU-bv2k5txExP8EH3ScUfGqtW1P3syThD84Z-g9k/edit#gid=0")
loqui_usage %>% count(email) %>% dplyr::pull(email) %>% length()
```

### Number of videos made with Loqui

```{r, message = FALSE}
loqui_usage %>% count(email) %>% dplyr::pull(n) %>% sum()
```

## Collect Calendly info 

```{r}
calendly_user <- get_calendly_user()
calendly_events <- list_calendly_events(user = calendly_user$resource$uri)

```

## Collect Workshop Feedback Info

```{r}
if (!file.exists(file.path("data", "itcr_slido_data.RDS"))) {
  itcr_drive_id <- "https://drive.google.com/drive/folders/0AJb5Zemj0AAkUk9PVA"
  itcr_slido_data <- get_slido_files(itcr_drive_id)

  saveRDS(itcr_slido_data, file.path("data", "itcr_slido_data.RDS"))
} else {
  itcr_slido_data <- readRDS(file.path("data", "itcr_slido_data.RDS"))
}
poll_data <- itcr_slido_data$`Polls-per-user` %>%
  janitor::clean_names()
```

## Data Visualizations

### How likely would you be to recommend this workshop?

```{r}
as.numeric(c(poll_data$how_likely_would_you_be_to_recommend_this_workshop, poll_data$how_likely_would_you_be_to_recommend_this_workshop_2)) %>%
  ggplot2::qplot(geom = "bar") +
  ggplot2::geom_bar(fill = "#CBC3E3") +
  ggplot2::theme_classic() +
  ggplot2::labs(title = "How likely would you be to recommend this workshop?")
  ggplot2::ggsave(file.path("plots", "itn_workshop_rec.png"), width = 4, height = 2)
```

### Workshop Relevance Feedback

```{r}
  poll_data <- poll_data %>%
    dplyr::filter(how_likely_are_you_to_use_what_you_learned_in_your_daily_work %in% c("Extremely likely", "Likely", "Not very likely", "Somewhat likely", "Very likely"))

  poll_data$how_likely_are_you_to_use_what_you_learned_in_your_daily_work <- factor(poll_data$how_likely_are_you_to_use_what_you_learned_in_your_daily_work, levels = c("Not very likely",  "Somewhat likely", "Likely", "Very likely", "Extremely likely"))

   ggplot2::ggplot(poll_data, ggplot2::aes(x = how_likely_are_you_to_use_what_you_learned_in_your_daily_work)) +
    ggplot2::geom_bar(stat = "count", fill = "#CBC3E3") +
    ggplot2::theme_classic() +
    ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
    ggplot2::labs(title = "How likely are you to use what you learned in your daily work?") +
    ggplot2::xlab("")
   ggplot2::ggsave(file.path("plots", "itn_relevance.png"), width = 4, height = 2)
```

### Wordclouds for Qualitative Workshop Feedback

```{r, results = 'hide'}
ud_model <- udpipe::udpipe_download_model(language = "english")
ud_model <- udpipe::udpipe_load_model(ud_model$file_model)
```

#### What did you like most about the workshop?

```{r}
results <- udpipe::udpipe_annotate(ud_model, x = poll_data$what_did_you_like_most_about_the_workshop) %>%
  as.data.frame() %>%
  dplyr::filter(upos %in% c("NOUN", "ADJ", "ADV")) %>%
  dplyr::mutate(lemma= tolower(lemma)) %>%
  dplyr::count(lemma)

wordcloud::wordcloud(words = results$lemma, freq=results$n,colors = c("#98fb98", "#83D475", "#355E3B"),
          min.freq = 3, scale = c(3, .4))
```

#### Please share any recommendations you have for improvements

```{r}
rec_results <- udpipe::udpipe_annotate(ud_model, x = poll_data$please_share_any_recommendations_you_have_for_improvements) %>%
  as.data.frame() %>%
  dplyr::filter(upos %in% c("NOUN", "ADJ", "ADV")) %>%
  dplyr::mutate(lemma= tolower(lemma)) %>%
  dplyr::count(lemma)

wordcloud::wordcloud(words = rec_results$lemma, freq=rec_results$n,colors = c("#98fb98", "#83D475", "#355E3B"),
          min.freq = 3, scale = c(4, .4))
```

## Get number of unique workshop attendees

```{r}
unique_emails <-
  unique(c(itcr_slido_data$`Polls-per-user`$`Please submit your email so we can log your attendance`,
           itcr_slido_data$`Polls-per-user`$`What's your email?`,
           itcr_slido_data$`Polls-per-user`$`What is your email?`))

length(unique_emails)
```

## Unique visitors to websites

```{r}
ggplot2::ggplot(ga_metrics, ggplot2::aes(x = reorder(website, -activeUsers), y = activeUsers)) +
  ggplot2::geom_bar(stat = "identity", fill = "lightgreen") +
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
  ggplot2::xlab("") +
  ggplot2::geom_text(ggplot2::aes(label = activeUsers), size = 3, vjust = - 1) +
  ggplot2::ylim(c(0, 6000))
  ggplot2::ggsave(file.path("plots", "itn_website_visits.png"), width = 4, height = 3)
```
## Table of user engagement

```{r}
user_totals <- ga_metrics %>% 
  janitor::clean_names() %>% 
  dplyr::select(website, active_users, average_session_duration) %>% 
  knitr::kable(digits=2, long_table = TRUE,padding = 2) %>%
  kableExtra::kable_styling(latex_options = c("striped", "scale_down"))

user_totals %>%
  kableExtra::save_kable(file.path("plots/course_user_table.pdf"))

user_totals
```

```{r}
user_engagement <- ga_metrics %>% 
  janitor::clean_names() %>% 
  dplyr::select(website, screen_page_views_per_user, sessions, average_session_duration, screen_page_views) %>% 
  knitr::kable(digits=2, long_table = TRUE, padding = 2) %>%
  kableExtra::kable_styling(latex_options = c("striped", "scale_down"))

user_engagement %>%
  kableExtra::save_kable("plots/course_engagement_table.pdf")

user_engagement
```

## ITN Course and Website Traffic Overtime 

```{r}
web_traffic_overtime <- ga_dims %>% 
  dplyr::mutate(date = lubridate::ymd(paste0(year, "-", month, "-", day))) %>% 
  dplyr::mutate(month_year = lubridate::ym(paste0(year, "-", month))) %>% 
  dplyr::mutate(web_yn = dplyr::case_when(
    website == "ITN Website" ~ "ITN Website", 
    website != "ITN Website" ~ "ITN Online Course Website"))

traffic_plot <- web_traffic_overtime %>% 
  dplyr::filter(website != "ITN Website") %>% 
  dplyr::group_by(month_year) %>% 
  dplyr::count() %>% 
  ggplot2::ggplot(ggplot2::aes(y = n, x = month_year)) + 
  ggplot2::geom_bar(stat = "identity", fill = "pink") + 
  ggplot2::scale_x_date(date_labels = "%b %Y") + 
  ggplot2::ylab("ITN Website Visits Overtime") +
  ggplot2::xlab("") +
  ggplot2::theme_minimal() +
  ggplot2::theme(axis.text.x=ggplot2::element_text(angle=60, hjust=1))

ggplot2::ggsave(file.path("plots", "itn_course_traffic_plot.png"), width = 4, height = 2)
  
traffic_plot
```

### Course traffic by course

```{r}
web_traffic_overtime %>% 
  dplyr::group_by(website, month_year) %>% 
  dplyr::count() %>% 
ggplot2::ggplot(ggplot2::aes(y = n, x = month_year)) + 
  ggplot2::geom_bar(stat = "identity", fill = "lightgreen") + 
  ggplot2::scale_x_date(date_labels = "%b %Y") + 
  ggplot2::ylab("Unique ITN Website Learners Overtime") +
  ggplot2::theme_minimal() +
  ggplot2::theme(axis.text.x=ggplot2::element_text(angle=60, hjust=1), 
                 strip.text.x = ggplot2::element_text(size = 8)) + 
  ggplot2::facet_wrap(~website) 

ggplot2::ggsave(file.path("plots", "itn_course_traffic_plot_by_course.png"), width = 10, height = 5)
```


## Coursera

```{r}
ggplot2::ggplot(itcr_course_data %>% dplyr::filter(total_coursera_enrollments > 0), ggplot2::aes(x = reorder(website, -total_coursera_enrollments), y = total_coursera_enrollments)) +
  ggplot2::geom_bar(stat = "identity", fill = "#89CFF0", na.rm = TRUE) +
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
  ggplot2::xlab("") +
  ggplot2::ylab("Coursera enrollments") +
  ggplot2::geom_text(ggplot2::aes(label = total_coursera_enrollments), size = 3, vjust = - 1, na.rm = TRUE) +
  ggplot2::ylim(c(0, 1200))
  ggplot2::ggsave(file.path("plots", "itn_coursera_enrollments.png"), width = 4, height = 2)
```

## Leanpub

```{r}
ggplot2::ggplot(itcr_course_data %>% dplyr::filter(total_leanpub_enrollees > 0) , ggplot2::aes(x = reorder(website, -total_leanpub_enrollees), y = total_leanpub_enrollees)) +
  ggplot2::geom_bar(stat = "identity", fill = "#89CFF0", na.rm = TRUE) +
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
  ggplot2::xlab("") +
  ggplot2::ylab("Leanpub enrollments") +
  ggplot2::geom_text(ggplot2::aes(label = total_leanpub_enrollees), size = 3, vjust = - 1, na.rm = TRUE) +
  ggplot2::ylim(c(0, 40))
ggplot2::ggsave(file.path("plots", "itn_leanpub_enrollments.png"), width = 4, height = 2)
```

## Learning Modalities

```{r}
totals <- data.frame(
  learners = c(
    sum(itcr_course_data$activeUsers, na.rm = TRUE),
    sum(itcr_course_data$total_coursera_enrollments, na.rm = TRUE),
    sum(itcr_course_data$total_leanpub_enrollees, na.rm = TRUE)),
  modality = c("website", "Coursera", "Leanpub"))
```

### Total learners from each platform

```{r}
ggplot2::ggplot(totals , ggplot2::aes(x = reorder(modality, -learners), y = learners)) +
  ggplot2::geom_bar(stat = "identity", fill = "lavender", na.rm = TRUE) +
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
  ggplot2::xlab("") +
  ggplot2::ylab("Visitors/Enrollees") +
  ggplot2::geom_text(ggplot2::aes(label = learners), size = 3, vjust = - 1, na.rm = TRUE)
ggplot2::ggsave(file.path("plots", "itn_total_enrollments.png"), width = 4, height = 2)
```

### Session Info 

```{r}
sessionInfo()
```
