---
title: "ITN Eval Metrics"
author: "Candace Savonen"
date: "2024-01-05"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# A first quick stab for collecting metrics on ITN happenings.

```{r}
dir.create("data", showWarnings = FALSE)
dir.create("plots", showWarnings = FALSE)
```

```{r}
devtools::load_all("../metricminer/")
#authorize("google")

accounts <- get_ga_user()
```

## Collect google analytics

```{r}
if (!file.exists(file.path("data", "itcr_ga_data.RDS"))) {
  fhdsl_stats_list <- all_ga_metrics(account_id = accounts$id[2])
  itcr_stats_list <- all_ga_metrics(account_id = accounts$id[5])

  all_data <- dplyr::bind_rows(fhdsl_stats_list$metrics ,itcr_stats_list$metrics)

  saveRDS(all_data, file.path("data","itcr_ga_data.RDS"))
} else {
  all_data <- readRDS(file.path("data","itcr_ga_data.RDS"))
}
```

# Collect coursera numbers by hand -- there's no API

```{r}
coursera_numbers <- c(
  "AI in Software" = 137,
  "Leadership Course" = 623,
  "Documentation and Usability Course" = 284,
  "Computing" = 931,
  "Reproducibility" = 359,
  "Advanced Reproducibility in Cancer Informatics" = 264
) %>%
  data.frame() %>%
  tibble::rownames_to_column("website") %>%
  dplyr::rename("total_coursera_enrollments"= ".")
```

# Collect leanpub numbers by hand -- their API is limited

```{r}
leanpub_numbers <- c(
  "AI in Software" = 7,
  "Leadership Course" = 32,
  "Documentation and Usability Course" = 26,
  "Computing" = 20,
  "Reproducibility" = 12,
  "Advanced Reproducibility in Cancer Informatics" = 15,
  "Choosing Genomic Tools" = 13
) %>%
  data.frame() %>%
  tibble::rownames_to_column("website") %>%
  dplyr::rename("total_leanpub_enrollees"= ".")
```

# Filter out non ITCR websites

```{r}
itcr_data <- all_data %>%
  dplyr::filter(!(website %in% c("hutchdatasci", "whoiswho", "MMDS", "FH Cluster 101", "AnVIL_Researcher_Journey"))) %>%
  dplyr::left_join(coursera_numbers) %>%
  dplyr::left_join(leanpub_numbers) 

readr::write_tsv(itcr_data, file.path("data", "itcr_website_metrics.tsv"))
```

# Collect loqui data

```{r}
loqui_usage <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1G_HTU-bv2k5txExP8EH3ScUfGqtW1P3syThD84Z-g9k/edit#gid=0")
loqui_usage %>% count(email)
```

## Collect slido info

```{r}
if (!file.exists(file.path("data", "itcr_slido_data.RDS"))) {
  itcr_drive_id <- "https://drive.google.com/drive/folders/0AJb5Zemj0AAkUk9PVA"
  itcr_slido_data <- get_slido_files(itcr_drive_id)

  saveRDS(itcr_slido_data, file.path("data", "itcr_slido_data.RDS"))
} else {
  itcr_slido_data <- readRDS(file.path("data", "itcr_slido_data.RDS"))
}
poll_data <- itcr_slido_data$`Polls-per-user` %>%
  janitor::clean_names()
```

## Plots

### Slido plots 

```{r}
as.numeric(c(poll_data$how_likely_would_you_be_to_recommend_this_workshop, poll_data$how_likely_would_you_be_to_recommend_this_workshop_2)) %>%
  ggplot2::qplot(geom = "bar") +
  ggplot2::geom_bar(fill = "#CBC3E3") +
  ggplot2::theme_classic() +
  ggplot2::labs(title = "How likely would you be to recommend this workshop?")
  ggplot2::ggsave(file.path("plots", "itn_workshop_rec.png"), width = 4, height = 2)
```

### Workshop Relevance 

```{r}
  poll_data <- poll_data %>%
    dplyr::filter(how_likely_are_you_to_use_what_you_learned_in_your_daily_work %in% c("Extremely likely", "Likely", "Not very likely", "Somewhat likely", "Very likely"))

  poll_data$how_likely_are_you_to_use_what_you_learned_in_your_daily_work <- factor(poll_data$how_likely_are_you_to_use_what_you_learned_in_your_daily_work, levels = c("Not very likely",  "Somewhat likely", "Likely", "Very likely", "Extremely likely"))
```

```{r}
   ggplot2::ggplot(poll_data, ggplot2::aes(x = how_likely_are_you_to_use_what_you_learned_in_your_daily_work)) +
    ggplot2::geom_bar(stat = "count", fill = "#CBC3E3") +
    ggplot2::theme_classic() +
    ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
    ggplot2::labs(title = "How likely are you to use what you learned in your daily work?") +
    ggplot2::xlab("")
   ggplot2::ggsave(file.path("plots", "itn_relevance.png"), width = 4, height = 2)

itcr_slido_data$JoinedParticipants %>% dplyr::count(event_name)
```

### Wordclouds

```{r}
ud_model <- udpipe::udpipe_download_model(language = "english")
ud_model <- udpipe::udpipe_load_model(ud_model$file_model)
```

```{r}
results <- udpipe::udpipe_annotate(ud_model, x = poll_data$what_did_you_like_most_about_the_workshop) %>%
  as.data.frame() %>%
  dplyr::filter(upos %in% c("NOUN", "ADJ", "ADV")) %>%
  dplyr::mutate(lemma= tolower(lemma)) %>%
  dplyr::count(lemma)

wordcloud::wordcloud(words = results$lemma, freq=results$n,colors = c("#98fb98", "#83D475", "#355E3B"),
          min.freq = 3, scale = c(3, .4))
```

```{r}
rec_results <- udpipe::udpipe_annotate(ud_model, x = poll_data$please_share_any_recommendations_you_have_for_improvements) %>%
  as.data.frame() %>%
  dplyr::filter(upos %in% c("NOUN", "ADJ", "ADV")) %>%
  dplyr::mutate(lemma= tolower(lemma)) %>%
  dplyr::count(lemma)

wordcloud::wordcloud(words = rec_results$lemma, freq=rec_results$n,colors = c("#98fb98", "#83D475", "#355E3B"),
          min.freq = 3, scale = c(4, .4))
```

## Get unique worshop attendees

```{r}
unique_emails <-
  unique(c(itcr_slido_data$`Polls-per-user`$`Please submit your email so we can log your attendance`,
           itcr_slido_data$`Polls-per-user`$`What's your email?`,
           itcr_slido_data$`Polls-per-user`$`What is your email?`))

length(unique_emails)
```

## Bookdown visits

```{r}
ggplot2::ggplot(itcr_data, ggplot2::aes(x = reorder(website, -activeUsers), y = activeUsers)) +
  ggplot2::geom_bar(stat = "identity", fill = "#89CFF0") +
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
  ggplot2::xlab("") +
  ggplot2::geom_text(ggplot2::aes(label = activeUsers), size = 3, vjust = - 1) +
  ggplot2::ylim(c(0, 5500))
  ggplot2::ggsave(file.path("plots", "itn_website_visits.png"), width = 4, height = 2)
```

## Coursera

```{r}
ggplot2::ggplot(itcr_data %>% dplyr::filter(total_coursera_enrollments > 0), ggplot2::aes(x = reorder(website, -total_coursera_enrollments), y = total_coursera_enrollments)) +
  ggplot2::geom_bar(stat = "identity", fill = "#89CFF0", na.rm = TRUE) +
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
  ggplot2::xlab("") +
  ggplot2::ylab("Coursera enrollments") +
  ggplot2::geom_text(ggplot2::aes(label = total_coursera_enrollments), size = 3, vjust = - 1, na.rm = TRUE) +
  ggplot2::ylim(c(0, 1200))
  ggplot2::ggsave(file.path("plots", "itn_coursera_enrollments.png"), width = 4, height = 2)
```

## Leanpub

```{r}
ggplot2::ggplot(itcr_data%>% dplyr::filter(total_leanpub_enrollees > 0) , ggplot2::aes(x = reorder(website, -total_leanpub_enrollees), y = total_leanpub_enrollees)) +
  ggplot2::geom_bar(stat = "identity", fill = "#89CFF0", na.rm = TRUE) +
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
  ggplot2::xlab("") +
  ggplot2::ylab("Leanpub enrollments") +
  ggplot2::geom_text(ggplot2::aes(label = total_leanpub_enrollees), size = 3, vjust = - 1, na.rm = TRUE) +
  ggplot2::ylim(c(0, 40))
ggplot2::ggsave(file.path("plots", "itn_leanpub_enrollments.png"), width = 4, height = 2)
```

## Learning Modalities

```{r}
totals <- data.frame(
  learners = c(
    sum(itcr_data$activeUsers, na.rm = TRUE),
    sum(itcr_data$total_coursera_enrollments, na.rm = TRUE),
    sum(itcr_data$total_leanpub_enrollees, na.rm = TRUE)), 
  modality = c("website", "Coursera", "Leanpub"))
```

```{r}
ggplot2::ggplot(totals , ggplot2::aes(x = reorder(modality, -learners), y = learners)) +
  ggplot2::geom_bar(stat = "identity", fill = "lavender", na.rm = TRUE) +
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust=1)) +
  ggplot2::xlab("") +
  ggplot2::ylab("Visitors/Enrollees") +
  ggplot2::geom_text(ggplot2::aes(label = learners), size = 3, vjust = - 1, na.rm = TRUE) 
ggplot2::ggsave(file.path("plots", "itn_total_enrollments.png"), width = 4, height = 2)
```
